Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-03-21 src/tex/ms.tex
Manuscript updates

\begin{figure*}
    \centering
    \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (e). Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. The median APOGEE abundance uncertainties were forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex. Model (a) assumes the fiducial parameters and the \yZ{1} yield set, whereas models (b--d) assume the \yZ{2} yield set. Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$. The distributions from APOGEE DR17 are plotted in column (e) for reference.}
    \label{fig:ofe-df}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models. Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius. A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates from APOGEE stars come from \citet{leung_variational_2023}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.}
    \label{fig:abundance-evolution}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk. Each panel presents the normalized stellar [Fe/H] distribution within a {2 kpc}-wide annulus, color-coded by the age bin. Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}). A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference. Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages. Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex}.}
    \label{fig:mdf-evolution}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models (a--d) and as observed by APOGEE (e). Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right. Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex. Model (a) assumes the fiducial parameters and the \yZ{1} yield set, whereas models (b--d) assume the \yZ{2} yield set. Model (c) also adopts a power-law SN Ia DTD, while in model (d) the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$. {\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent when assuming higher yields and outflows. This effect can be mitigated by pre-enriched infall.}
    \label{fig:ofe-df}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models. Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius. A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates from APOGEE stars come from \citet{leung_variational_2023}. Each column shows results from a different multi-zone model: {\bf (a)} a model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with $y/Z_\odot=1$ and greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model with $y/Z_\odot=1$ and which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$. {\bf Key takeaway:} All models feature a major dilution event at a lookback time of 9 Gyr, and for models with low yields and outflows the dilution persists throughout much of the thin disk epoch.}
    \label{fig:abundance-evolution}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk. Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age. Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}). A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference. Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages. Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity. {\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
    \label{fig:mdf-evolution}
\end{figure*}
